\textcolor{red}{Simple} connectome inference using partial correlation from imaging calcium signal

### 2014-06-16 article.tex
improve high pass filter

The raw signal (original signal of Figure \ref{fig:fitlering}) is very noisy
due to light scattering artifacts that ordinarily affects the quality of the
recording (\cite{lichtman2011big}). A low-pass filter is first applied to
filter high frequency noise with one of the following designs
\begin{align}
% symmetrical median filter
x^t_i &\leftarrow x^{t-1}_i + x^{t}_i + x^{t+1}_i \label{eq:symetric-median}, \\
% asymmetrical weighted median
x^t_i &\leftarrow 0.4 x^{t-3}_i + 0.6 x^{t-2}_i + 0.8 x^{t-1}_i + x_{t}^i.
\label{eq:weighted-asymetric-median}.
\end{align}

Considering the short delay for a communication between
neurons, slow events can be neglected to retrieve direct relationships.
Indeed, for a direct relationship, i.e. a neuron firing directly implying another
neuron to fire, the average time is about $1ms$ or $2ms$ while the
fluorescent signal time resolution is $20ms$. In order to find out which neurons
are directly related, it is only necessary to look after the burst signal, or
in other words, whether the signal varies. In our approach, we choose to apply
an asymmetrical discrete derivative : $x^{t,d}_{i} \leftarrow x^{t}_i - x^{t-1}_i$.

>>>>

The raw signal (original signal of Figure \ref{fig:fitlering}) is very noisy
due to light scattering artifacts that ordinarily affects the quality of the
recording (\cite{lichtman2011big}). A low-pass filter is first applied to
filter high frequency noises with one of the following filter designs
\begin{align}
% symmetrical median filter
x^t_i &\leftarrow x^{t-1}_i + x^{t}_i + x^{t+1}_i \label{eq:symetric-median}, \\
% asymmetrical weighted median
x^t_i &\leftarrow 0.4 x^{t-3}_i + 0.6 x^{t-2}_i + 0.8 x^{t-1}_i + x_{t}^i.
\label{eq:weighted-asymetric-median}.
\end{align}

A neuron spike lasts on average $1ms$ to $2ms$, while current optical
device have a time resolution of $20ms$. Considering the short delay for a
communication between neurons and slow decay of fluorescence signal, we
can filter low frequencies through an asymmetrical discrete derivative filter
\begin{align}
x^{t,d}_{i} \leftarrow x^{t}_i - x_{t-1}^i.
\end{align}
When slow signals variations are filtered (H-P signals of figure
\ref{fig:filtering}), only remains spike positions.
\textcolor{red}{Pourquoi sur la figure, on a pas de signal avec une dérivée
                négative?}
